### 2015-01-12 src/analysis.Rnw
tables

>>>>

\begin{table}[!ht]
\caption*{Selective}
<<results='asis'>>=
print(xtable(r.selective.db, caption='Selective', label='table:selective'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The operator selection criteria results. }
\label{tbl:lcountl}
\end{table}

\begin{table}[!ht]
\caption*{Element Scoped}
<<results='asis'>>=
print(xtable(r.lmc.db, caption='Element Scoped', label='table:element'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The element based sampling criteria results. }
\label{tbl:lcountl}
\end{table}

\begin{table}[!ht]
\caption*{N-Selection}
<<results='asis'>>=
print(xtable(r.nselection.db, caption='N-Selection', label='table:nselection'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The n-selection criteria results}
\label{tbl:lcountl}
\end{table}

\begin{table}[!ht]
\caption*{Single Operators}
<<results='asis'>>=
print(xtable(r.singles.db, caption='Single Operators', label='table:singles'), include.rownames=T, floating=F, size='\\small',sanitize.text.function=function(x){x})
@
\caption {The n-selection criteria results}
\label{tbl:lcountl}
\end{table}

### 2015-01-12 src/introduction.Rnw
tables

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
250 Java programs from Github\footnote{Our dataset is 322 programs, but as of
this writing the larger projects have not completed finished running
full-mutation analysis.},
with size ranging from 50 LOC to 100 KLOC, excluding tests,
which should allow widely applicable statistical inferences to be made.

>>>>

We have attempted to rectify this situation with a large scale study of real
world programs. As detailed in Section~\ref{sec:methodology}, we sample
250 Java programs from Github\footnote{Our dataset is 322 programs, but as of
this writing the larger projects have not completed finished running
full-mutation analysis.},
with size ranging from 50 LOC to 100 KLOC, excluding tests,
which allow widely applicable statistical inferences to be made.

For a mutation selection strategy to be considered effective, especially during
the development, it should be able to expose as many defect-like behaviors as
possible.
